### 2021-07-30 doc/thesis/chapters/results.tex
work on LOC plots.. (still wip...)

\includepicture [0.9] [0] {Lines of code of the respective system design parts, presented in a pie chart.} {lines_of_code_pie_chart} {img/matlab/lines_of_code_pie_chart_py}

>>>>

\begin{figure}%
  \centering
  \subfloat[\centering Overview of ]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py_all} }}%
  \\
  %\hspace{\fill}
  \subfloat[\centering HLS]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py_hls} }}%
  %\hspace{\fill}
  %\vspace{3cm}
  \subfloat[\centering VHDL]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py_vhdl} }}%

  \caption{Lines of code of the respective system design parts, presented in multiple pie charts.}%
  \label{fig:lines_of_code_pie_chart}%
\end{figure}
